\bf\mftitle

### 2011-02-01 doc/jInfer/architecture/architecture.tex
resolving todos in arch and twostep, and fresh rebuild of all pdfs

For these cases, special \code{getMutable()} method is implemented to obtain regexp with none of the members set. One has to fill in all properties carefully and call \code{setImmutable()} aftewards. Proper usage should be one of following: % TODO anti WTF?
Regexp instance is by default created as immutable, that is, once instantiated, you cannot add more children to list of children, cannot change type, content etc. In special circumstances, one does not know future children of regexp at the time of creation. This occurs mainly in input modules: while parsing XML data sequentially, one does not know contents of element in time of handling start element event.
\begin{verbatim}
	Regexp<T> r = Regexp.<T>getMutable();
	r.setInterval(...);
	r.setType(RegexpType.LAMBDA);
	r.setImmutable();cz.cuni.mff.ksi.jinfer.base
\end{verbatim}
\begin{verbatim}
	Regexp<T> r = Regexp.<T>getMutable();
	r.setInterval(...);
	r.setType(RegexpType.TOKEN);
	r.setContent(...)
	r.setImmutable();
\end{verbatim}
\begin{verbatim}
	Regexp<T> r = Regexp.<T>getMutable();
	r.setInterval(...);
	r.setType(RegexpType.CONCATENATION);
	r.addChild(...);
	r.addChild(...);
	r.addChild(...);
	r.setImmutable();
\end{verbatim}

@@

This modular architecture means that it is possible to replace any and/or all of these modules with \emph{something} else that does similar job. In practice, researchers will probably implement new \jmodule{Simplifier} modules, while using our implementation of BasicIGG and export modules. This modular scheme is also used inside our modules to divide them into submodules. It is possible to add new file format processing to import/export. One can extend automaton merging state algorithm of our implementation of \cite{ahonen} in TwoStepSimplifier module by replacing submodules. % TODO anti This is a terrible paragraph with no clear path to follow, please reorganize (sentences on their own are OK)

@@

\paragraph{Initial Grammar} has two formats:
\begin{itemize}
	\item \textbf{Only concatenations.} This is the default format. All regular expressions coming from IGG have to be concatenations, even if they are empty.
	When importing XML documents this is just fine, because a document is a positive example of language we are trying to identify.
	But while importing schemas, queries or other stuff that can contain more information, it might be necessary to convert it somehow to concatenations.
	For example, when importing DTD:
	\begin{verbatim}
	<!ELEMENT person (info?, more, more?, more?)>
	<!ELEMENT info (#PCDATA | note)*>
	<!ELEMENT note EMPTY>
	<!ELEMENT more EMPTY>
	\end{verbatim}
	% TODO anti Emphasise elements in the following paragraph
	Elements note and more are empty, but we cannot use lambda regexp. Import will use empty concatenation instead.
	For element person, import module has to generate some positive examples of language generated by regular expression \verb+(info?, more, more?, more?)+.

>>>>

Regexp instance is by default created as immutable, that is, once instantiated, you cannot add more children to list of children, cannot change type, content etc. In special circumstances, one does not know future children of regexp at the time of creation. This occurs mainly in input modules: while parsing XML data sequentially, one does not know contents of element in time of handling start element event.

For these cases, special \code{getMutable()} method is implemented to obtain regexp with none of the members set. One has to fill in all properties carefully and call \code{setImmutable()} aftewards. Proper usage should be one of following:
\begin{verbatim}
	Regexp<T> r = Regexp.<T>getMutable();
	r.setInterval(...);
	r.setType(RegexpType.LAMBDA);
	r.setImmutable();cz.cuni.mff.ksi.jinfer.base
\end{verbatim}
\begin{verbatim}
	Regexp<T> r = Regexp.<T>getMutable();
	r.setInterval(...);
	r.setType(RegexpType.TOKEN);
	r.setContent(...)
	r.setImmutable();
\end{verbatim}
\begin{verbatim}
	Regexp<T> r = Regexp.<T>getMutable();
	r.setInterval(...);
	r.setType(RegexpType.CONCATENATION);
	r.addChild(...);
	r.addChild(...);
	r.addChild(...);
	r.setImmutable();
\end{verbatim}

@@

@@

\paragraph{Initial Grammar} has two formats:
\begin{itemize}
	\item \textbf{Only concatenations.} This is the default format. All regular expressions coming from IGG have to be concatenations, even if they are empty.
	When importing XML documents this is just fine, because a document is a positive example of language we are trying to identify.
	But while importing schemas, queries or other stuff that can contain more information, it might be necessary to convert it somehow to concatenations.
	For example, when importing DTD:
	\begin{verbatim}
	<!ELEMENT person (info?, more, more?, more?)>
	<!ELEMENT info (#PCDATA | note)*>
	<!ELEMENT note EMPTY>
	<!ELEMENT more EMPTY>
	\end{verbatim}
	\emph{Elements} note and more are empty, but we cannot use lambda regexp. Import will use empty concatenation instead.
	For \emph{element} person, import module has to generate some positive examples of language generated by regular expression \verb+(info?, more, more?, more?)+.

### 2011-02-01 doc/jInfer/twostep/twostep.tex
resolving todos in arch and twostep, and fresh rebuild of all pdfs

% TODO anti Representant -> Representative!

@@

% TODO anti Rewrite so that these sentences don't end with "too" all the time
Under certain circumstances it is useful to declare method \code{create()} generic.
The \jmodule{AutomatonSimplifier} works with \code{Automaton} instances, which are generic too.
But automaton simplification does not depend on type of symbol of automaton transitions, so interface \code{AutomatonSimplifier<T>}
generic too.
Factory interface deals with this by defining the \code{create()} method generic.

@@

Method \code{TwoStepSimplifier.simplify()} basically does the following.
% TODO anti Rename finalGrammar to resultGrammar or something like that
\begin{verbatim}
// 1. cluster elements
Clusterer<AbstractStructuralNode> clusterer = clustererFactory.create();
clusterer.addAll(initialGrammar);
clusterer.cluster();

// 2. prepare emtpy final grammar
List<Element> finalGrammar= new LinkedList<Element>();

@@

for (Cluster<AbstractStructuralNode> cluster : clusterer.getClusters()) {
  AbstractStructuralNode node =  
                          processor.processCluster(clusterer, cluster.getMembers());
  RegularExpressionCleaner<AbstractStructuralNode> cleaner = 
                          regularExpressionCleanerFactory.<AbstractStructuralNode>create();
  // 4. add to rules
  finalGrammar.add(
              new Element(node.getContext(),
              node.getName(),
              node.getMetadata(),
              cleaner.cleanRegularExpression(((Element) node).getSubnodes()),
              attList));
}

return finalGrammar;
\end{verbatim}
First, it creates a clusterer, gives it all the rules and performs the clustering.
Then, empty list of elements is created as the final (simplified) grammar.
For each input rule in \code{initialGrammar}, submodule \jmodule{ClusterProcessor} is invoked to infer the regular expression of that element.
Finally, regular expression cleaning is done in a submodule and new \code{Element} instance is created as a copy of processed node, but with inferred and cleaned regexp.

@@

%#### STRUCTURE->Clusterer->WithAttributes ############################################
\subsubsection{ClustererWithAttributes extended interface}
You might have noticed that the \jmodule{Clusterer} interface and \code{Cluster} class are generic.
They may be used as design pattern not only for clustering elements in inference process.
To address clustering of elements in more detail, we created \code{Cluster\.er\.With\.At\.tri\.bu\.tes<T, S>} interface, which extends \code{Clusterer<T>} interface.
It adds method \code{List\.<Cluster<S>{}> get\.At\.tri\.bu\.teClusters(T representant)}, implying that each representant of
type \code{T} (that is representant of some main cluster) has some "attribute" clusters associated with it.
Attribute clusters are of type \code{S} and can be retrieved by calling \code{getAttributeClusters(x)}.

@@

% TODO anti Not clear what "worker" is
Worker interface itself is defined as follows.
\begin{verbatim}
public interface ClusterProcessor<T> {
  T processCluster(
          Clusterer<T> clusterer,
          List<T> rules
          ) throws InterruptedException;
}
\end{verbatim}
Why is the cluster processor given a clusterer instance?
Rules themselves contain information about which elements to process, but clusterer has more information about the topic.
Clusterer can tell you the representant for any element in the whole input (not only those elements in rules, but also those that may be on right side of rules). Also, clusterer (if it is with attributes) has information about attributes in each cluster.

@@

%#### DATA FLOW ############################################
\section{Data flow}
\begin{figure}[tpb]
	\centering\includegraphics[scale=1]{twostep_flow}
	\caption{TwoStep data flow} \label{twostep_flow}
\end{figure}
Process illustrated in fig. \ref{twostep_flow} is as follows.
\begin{enumerate}
	\item Initial Grammar on input, which is ruled into \jmodule{Clusterer}. % TODO anti WTF is "ruled into"?
	\item Each cluster is sent to submodule \jmodule{ClusterProcessor}, which returns regular expression for that cluster.
	\item Regular expression is sent to \jmodule{RegularExpressionCleaner} submodule for cleaning.
	\item Regular expressions representing all the processed clusters are added to the list of simplified grammar rules.
	\item List of simplified rules is returned (Simplified grammar).
\end{enumerate}

%#### SUBMODULES ############################################
\section{Submodule implementations}
%#### SUBMODULES->Iname ############################################
\subsection{Iname (ClusteterWithAttributes)} \label{section_Iname}
We cluster elements in \code{Iname<AbstractStructuralNode, Attribute>} class (Iname je clusterer!), which takes \code{AbstractStructuralNode} classes to cluster as main, and \code{Attribute} classes as attributes. % TODO anti I don't understand the sentence, rewrite.
Clustering is done based on element's \code{getName()} equality (ignoring case).
For each rule (element), it is first clustered by finding the cluster which representant has the same name - or create new cluster with this element as representant.
Then we process right side of this element rule (that are nodes from \code{getSubnodes()}).
Since right side of rule is always concatenation (\jmodule{TwoStep} accepts only simple grammar representation), we simply take \code{.getSubnodes().getTokens()} list and iterate through it.
Each node on right side, is examined in the following way.
\begin{itemize}
  \item If it is \textbf{simple data}, throw it to \code{SimpleDataClusterer} class which is associated with main element cluster. It does nothing more, than holds all \code{SimpleData} instances in one cluster. But in future it may be replaced to cluster simple data somehow, to obtain meaningful content models in schemas.
  \item If it is \textbf{element} and it is tagged as sentinel - search main clusters to find cluster with representant of same \code{getName()}, or create new cluster with this sentinel as representant. From IGG, sentinels may be only on right sides of rules and since each element in schemas has to be defined, there must exist another element with same name, which is not sentinel (and maybe it will come to process in future). So there can't be cluster with only one sentinel element in it. % TODO anti Please rewrite the really long sentence.
  \item Do nothing otherwise, since it is element, it has to have its subnodes defined, and therefore it is element that is proper grammar rule and therefore it has to be somewhere in Initial Grammar, thus it is already processed or is on schedule. % TODO anti Totally unclear, rewrite
\end{itemize}
Attributes of element are processed through a helper attribute clusterer, which is created for each element cluster.
We have bunch of elements of same name in a cluster and one attribute clusterer associated with this bunch.
This attribute clusterer is given all attributes instances encountered in all elements that are in bunch.
It clusters them by name, case insensitive.
Each main cluster also has \code{SimpleData} clusterer associated with it.
Whole scheme is on fig. \ref{clusterer_structure}.
\begin{figure}[tpb]
	\centering\includegraphics[scale=1]{clusterer_structure}
	\caption{Iname clusterer structure} \label{clusterer_structure}
\end{figure}

@@

%#### SUBMODULES->PassRepresentant ############################################
\subsection{PassRepresentant (ClusterProcessor)} \label{section_PassRepresentant}
Trivial ClusterProcessor implementation. For each cluster return its representant as the rule to be in resulting schema.
This has nothing to do with grammar simplification, it is just a proof-of-concept submodule.
Input documents are not valid against this odd grammar.
Do not use this in practice, just read the code to understand the bare minimum needed to implement a submodule.

@@

As you can see, it is important that class \code{T} has proper implementation of \code{.equals()} method, as symbols are tested for equality by calling this method on them.
By the way, this is why we cluster all simple data and all sentinels on right sides of rules.	
While adding a concatenation to the automaton, instead of the instances themselves their \emph{representatives} are used. See \ref{section_AutomatonMergingState_structure} for further reference.
This assures that comparisons in automaton are done using Java \code{Object.equals()} reference comparison, but for each cluster member, its representant is only present in automaton.
That results in cluster-equal behaviour.
Example of prefix-tree automaton is in fig. \ref{pta}.

@@

\subsubsection{AutomatonSimplifier module}
\jmodule{AutomatonSimplifier} module has its worker interface defined as following.
\begin{verbatim}
public interface AutomatonSimplifier<T> {
  Automaton<T> simplify(Automaton<T> inputAutomaton, 
                        SymbolToString<T> symbolToString) throws InterruptedException;
  Automaton<T> simplify(Automaton<T> inputAutomaton, 
                        SymbolToString<T> symbolToString,
                        String elementName) throws InterruptedException;
}
\end{verbatim}
Given input automaton it returns automaton, there is nothing magical to it.
Interface is defined as generic, implementations don't have to be. However, there is no reason not to make them generic.
When implementation needs to present an automaton to user, it needs string representation of symbols to display on automaton transitions.
For this reason, the second parameter, \code{symbolToString} (implementation of \code{SymbolToString} interaface) is given.
It is responsible for converting symbol to string.
% To \jmodule{AutomatonSimplifier} it is passed from \jmodule{AutomatonMergingState} cluster processor, where we know that symbols are of type \code{AbstractStructuralNode}, so we implement \code{SymbolToString} by using \code{getName()} method on nodes and pass it down to generic \code{AutomatonSimplififier} submodule. % TODO anti Unreadable....
Overloaded version is to inform the user about name of processed element when presenting automaton in \jmodule{AutoEditor}.
This version of interface will probably change in future.

@@

\subsection{StateRemoval (RegexpAutomatonSimplifier)} \label{section_StateRemoval}
\begin{wrapfigure}{R}{40mm}
	\centering\includegraphics[scale=\myscale]{state_removal_modules}
	\caption{Modules of StateRemoval.} \label{state_removal_modules}
	\vspace{10mm}
\end{wrapfigure}
We are using state removal method (see \cite{1224321}) to convert regexp automaton into equivalent regular expression.
This is implemented in \code{StateRemoval} class (on fig. \ref{state_removal_modules}) which implements \code{RegexpAutomatonSimplifier} interface.
% TODO anti Emphasise the states in following sentences
Before the algorithm starts, states superInitial and superFinal are added to automaton, former with $\lambda$-transition to initial state.
From all final states a $\lambda$ transition to superFinal state is added.
State removal works by removing states of automaton (and redirecting transitions properly) until there are last to two states - superInitial and superFinal.
After removing all states, there is only one transition from superInitial to superFinal state.
That transition has the final regular expression as symbol on it. This one is returned.

@@

\subsubsection{Data Structures - StateRemovalRegexpAutomaton}
We extend \code{RegexpAutomaton} to obtain automaton that fits the state removal procedure.
This implementation has methods \code{crea\.te\.Su\.per\.In\.it\.ial\.Sta\.te} and \code{crea\.te\.Su\.per\.In\.it\.ial\.Sta\.te}.
They does exactly what their names stands for.
% TODO anti Emphasise the states again
SuperInitial state has only one $\lambda$-out-transition pointing to original initial state.
SuperFinal state has as many $\lambda$-in-transitions, as there are original final states - from each one it gets one.
Without going further into many technical details, we just mention method \code{removeState}, which removes given state from automaton.
Transitions are handled in the following way.
\begin{enumerate}
	\item Collapse all loop transitions of removed state to one loop transition with new \code{Regex.ALTERNATION} of all regexps on original loops (with Kleene interval set).
	\item Collapse all {in | out}-transitions, which same {source | destination} state to one transition with \code{Reg\.exp.AL\.TER\.NA\.TION} of original regexps.
	\item For each in-transition, loop, and out-transition, add transition from in-transition source to out-transition destination with symbol of \code{Regexp.CONCATENATION} of in-transition regexp, loop regexp and out-transition regexp. Thus by-passing the state completely.
	\item Remove the state and transitions associated with it.
\end{enumerate}
The whole process is step-by-step illustrated in fig. \ref{regaut}.
\begin{figure}[pb]
	\centering
	\subfigure[RegexpAutomaton after conversion from ordinary automaton.]
	{
		\includegraphics[scale=\myscale]{regaut1}
		\label{regaut1}
	}
	\subfigure[First, collapse loop transitions to alternation with Kleene interval set.]
	{
		\includegraphics[scale=\myscale]{regaut2}
		\label{regaut2}
	}
	\subfigure[Collapse {in | out}-transitions {from | to} same states.]
	{
		\includegraphics[scale=\myscale]{regaut3}
		\label{regaut3}
	}
	\subfigure[Bypass state 3 by adding concatenation transitions from states 1 and 2 to state 4. Remove state 3 and associated transitions.]
	{
		\includegraphics[scale=\myscale]{regaut4}
		\label{regaut4}
	}
%	
%	\subfigure[Finally remove state 3 and associated transitions.]
%	{
%		\includegraphics[scale=\myscale]{regaut5}
%		\label{regaut5}
%	}
	\caption{RegexpAutomaton and removing state 3 from it.} \label{regaut}
\end{figure}

>>>>

@@

Under certain circumstances it is useful to declare method \code{create()} generic.
The \jmodule{AutomatonSimplifier} works with \code{Automaton} instances, which are generic.
But automaton simplification does not depend on type of symbol of automaton transitions, so interface \code{AutomatonSimplifier<T>}
generic too.
Factory interface deals with this by defining the \code{create()} method generic.

@@

Method \code{TwoStepSimplifier.simplify()} basically does the following.
\begin{verbatim}
// 1. cluster elements
Clusterer<AbstractStructuralNode> clusterer = clustererFactory.create();
clusterer.addAll(initialGrammar);
clusterer.cluster();

// 2. prepare emtpy simplified grammar
List<Element> simplifiedGrammar= new LinkedList<Element>();

@@

for (Cluster<AbstractStructuralNode> cluster : clusterer.getClusters()) {
  AbstractStructuralNode node =  
                          processor.processCluster(clusterer, cluster.getMembers());
  RegularExpressionCleaner<AbstractStructuralNode> cleaner = 
                          regularExpressionCleanerFactory.<AbstractStructuralNode>create();
  // 4. add to rules
  simplifiedGrammar.add(
              new Element(node.getContext(),
              node.getName(),
              node.getMetadata(),
              cleaner.cleanRegularExpression(((Element) node).getSubnodes()),
              attList));
}

return simplifiedGrammar;
\end{verbatim}
First, it creates a clusterer, gives it all the rules and performs the clustering.
Then, empty list of elements is created as the simplified grammar.
For each input rule in \code{initialGrammar}, submodule \jmodule{ClusterProcessor} is invoked to infer the regular expression of that element.
Finally, regular expression cleaning is done in a submodule and new \code{Element} instance is created as a copy of processed node, but with inferred and cleaned regexp.

@@

%#### STRUCTURE->Clusterer->WithAttributes ############################################
\subsubsection{ClustererWithAttributes extended interface}
You might have noticed that the \jmodule{Clusterer} interface and \code{Cluster} class are generic.
They may be used as design pattern not only for clustering elements in inference process.
To address clustering of elements in more detail, we created \code{Cluster\.er\.With\.At\.tri\.bu\.tes<T, S>} interface, which extends \code{Clusterer<T>} interface.
It adds method \code{List\.<Cluster<S>{}> get\.At\.tri\.bu\.teClusters(T representant)}, implying that each representative of
type \code{T} (that is representative of some main cluster) has some "attribute" clusters associated with it.
Attribute clusters are of type \code{S} and can be retrieved by calling \code{getAttributeClusters(x)}.

@@

Interface of submodule is defined as follows.
\begin{verbatim}
public interface ClusterProcessor<T> {
  T processCluster(
          Clusterer<T> clusterer,
          List<T> rules
          ) throws InterruptedException;
}
\end{verbatim}
Why is the cluster processor given a clusterer instance?
Rules themselves contain information about which elements to process, but clusterer has more information about the topic.
Clusterer can tell you the representative for any element in the whole input (not only those elements in rules, but also those that may be on right side of rules). Also, clusterer (if it is with attributes) has information about attributes in each cluster.

@@

%#### DATA FLOW ############################################
\section{Data flow}
\begin{figure}[tpb]
	\centering\includegraphics[scale=1]{twostep_flow}
	\caption{TwoStep data flow} \label{twostep_flow}
\end{figure}
Process illustrated in fig. \ref{twostep_flow} is as follows.
\begin{enumerate}
	\item Initial Grammar on input, which is sent into \jmodule{Clusterer}.
	\item Each cluster is sent to submodule \jmodule{ClusterProcessor}, which returns regular expression for that cluster.
	\item Regular expression is sent to \jmodule{RegularExpressionCleaner} submodule for cleaning.
	\item Regular expressions representing all the processed clusters are added to the list of simplified grammar rules.
	\item List of simplified rules is returned (Simplified grammar).
\end{enumerate}

%#### SUBMODULES ############################################
\section{Submodule implementations}
%#### SUBMODULES->Iname ############################################
\subsection{Iname (ClusteterWithAttributes)} \label{section_Iname}
We cluster elements in \code{Iname<AbstractStructuralNode, Attribute>} class (Iname je clusterer!), which takes \code{AbstractStructuralNode} classes to cluster as main, and \code{Attribute} classes as attributes. % TODO anti I don't understand the sentence, rewrite.
Clustering is done based on element's \code{getName()} equality (ignoring case).
For each rule (element), it is first clustered by finding the cluster which representative has the same name - or create new cluster with this element as representative.
Then we process right side of this element rule (that are nodes from \code{getSubnodes()}).
Since right side of rule is always concatenation (\jmodule{TwoStep} accepts only simple grammar representation), we simply take \code{.getSubnodes().getTokens()} list and iterate through it.
Each node on right side, is examined in the following way.
\begin{itemize}
  \item If it is \textbf{simple data}, throw it to \code{SimpleDataClusterer} class which is associated with main element cluster. It does nothing more, than holds all \code{SimpleData} instances in one cluster. But in future it may be replaced to cluster simple data somehow, to obtain meaningful content models in schemas.
  \item If it is \textbf{element} and it is tagged as sentinel - search main clusters to find cluster with representative of same \code{getName()}, or create new cluster with this sentinel as representative. From IGG, sentinels may be only on right sides of rules and since each element in schemas has to be defined, there must exist another element with same name, which is not sentinel (and maybe it will come to process in future). So there can't be cluster with only one sentinel element in it. % TODO anti Please rewrite the really long sentence.
  \item Do nothing otherwise, since it is element, it has to have its subnodes defined, and therefore it is element that is proper grammar rule and therefore it has to be somewhere in Initial Grammar, thus it is already processed or is on schedule. % TODO anti Totally unclear, rewrite
\end{itemize}
Attributes of element are processed through a helper attribute clusterer, which is created for each element cluster.
We have bunch of elements of same name in a cluster and one attribute clusterer associated with this bunch.
This attribute clusterer is given all attributes instances encountered in all elements that are in bunch.
It clusters them by name, case insensitive.
Each main cluster also has \code{SimpleData} clusterer associated with it.
Whole scheme is on fig. \ref{clusterer_structure}.
\begin{figure}[tpb]
	\centering\includegraphics[scale=1]{clusterer_structure}
	\caption{Iname clusterer structure} \label{clusterer_structure}
\end{figure}

@@

%#### SUBMODULES->PassRepresentant ############################################
\subsection{PassRepresentant (ClusterProcessor)} \label{section_PassRepresentant}
Trivial ClusterProcessor implementation. For each cluster return its representative as the rule to be in resulting schema.
This has nothing to do with grammar simplification, it is just a proof-of-concept submodule.
Input documents are not valid against this odd grammar.
Do not use this in practice, just read the code to understand the bare minimum needed to implement a submodule.

@@

As you can see, it is important that class \code{T} has proper implementation of \code{.equals()} method, as symbols are tested for equality by calling this method on them.
By the way, this is why we cluster all simple data and all sentinels on right sides of rules.	
While adding a concatenation to the automaton, instead of the instances themselves their \emph{representatives} are used. See \ref{section_AutomatonMergingState_structure} for further reference.
This assures that comparisons in automaton are done using Java \code{Object.equals()} reference comparison, but for each cluster member, its representative is only present in automaton.
That results in cluster-equal behaviour.
Example of prefix-tree automaton is in fig. \ref{pta}.

@@

\subsubsection{AutomatonSimplifier module}
\jmodule{AutomatonSimplifier} module has its worker interface defined as following.
\begin{verbatim}
public interface AutomatonSimplifier<T> {
  Automaton<T> simplify(Automaton<T> inputAutomaton, 
                        SymbolToString<T> symbolToString) throws InterruptedException;
  Automaton<T> simplify(Automaton<T> inputAutomaton, 
                        SymbolToString<T> symbolToString,
                        String elementName) throws InterruptedException;
}
\end{verbatim}
Given input automaton it returns automaton, there is nothing magical to it.
Interface is defined as generic, implementations don't have to be. However, there is no reason not to make them generic.
When implementation needs to present an automaton to user, it needs string representation of symbols to display on automaton transitions.
For this reason, the second parameter, \code{symbolToString} (implementation of \code{SymbolToString} interaface) is given.
It is responsible for converting symbol to string.
Overloaded version is to inform the user about name of processed element when presenting automaton in \jmodule{AutoEditor}.
This version of interface will probably change in future.

@@

\subsection{StateRemoval (RegexpAutomatonSimplifier)} \label{section_StateRemoval}
\begin{wrapfigure}{R}{40mm}
	\centering\includegraphics[scale=\myscale]{state_removal_modules}
	\caption{Modules of StateRemoval.} \label{state_removal_modules}
	\vspace{10mm}
\end{wrapfigure}
We are using state removal method (see \cite{1224321}) to convert regexp automaton into equivalent regular expression.
This is implemented in \code{StateRemoval} class (on fig. \ref{state_removal_modules}) which implements \code{RegexpAutomatonSimplifier} interface.
Before the algorithm starts, states \emph{superInitial} and \emph{superFinal} are added to automaton, former with $\lambda$-transition to initial state.
From all final states a $\lambda$ transition to \emph{superFinal} state is added.
State removal works by removing states of automaton (and redirecting transitions properly) until there are last to two states - \emph{superInitial} and \emph{superFinal}.
After removing all states, there is only one transition from \emph{superInitial} to \emph{superFinal} state.
That transition has the final regular expression as symbol on it. This one is returned.

@@

\subsubsection{Data Structures - StateRemovalRegexpAutomaton}
We extend \code{RegexpAutomaton} to obtain automaton that fits the state removal procedure.
This implementation has methods \code{crea\.te\.Su\.per\.In\.it\.ial\.Sta\.te} and \code{crea\.te\.Su\.per\.In\.it\.ial\.Sta\.te}.
They does exactly what their names stands for.
\emph{SuperInitial} state has only one $\lambda$-out-transition pointing to original initial state.
\emph{SuperFinal} state has as many $\lambda$-in-transitions, as there are original final states - from each one it gets one.
Without going further into many technical details, we just mention method \code{removeState}, which removes given state from automaton.
Transitions are handled in the following way.
\begin{enumerate}
	\item Collapse all loop transitions of removed state to one loop transition with new \code{Regex.ALTERNATION} of all regexps on original loops (with Kleene interval set).
	\item Collapse all {in | out}-transitions, which same {source | destination} state to one transition with \code{Reg\.exp.AL\.TER\.NA\.TION} of original regexps.
	\item For each in-transition, loop, and out-transition, add transition from in-transition source to out-transition destination with symbol of \code{Regexp.CONCATENATION} of in-transition regexp, loop regexp and out-transition regexp. Thus by-passing the state completely.
	\item Remove the state and transitions associated with it.
\end{enumerate}
The whole process is step-by-step illustrated in fig. \ref{regaut}.
\begin{figure}[pb]
	\centering
	\subfigure[RegexpAutomaton after conversion from ordinary automaton.]
	{
		\includegraphics[scale=\myscale]{regaut1}
		\label{regaut1}
	}
	\subfigure[First, collapse loop transitions to alternation with Kleene interval set.]
	{
		\includegraphics[scale=\myscale]{regaut2}
		\label{regaut2}
	}
	\subfigure[Collapse {in | out}-transitions {from | to} same states.]
	{
		\includegraphics[scale=\myscale]{regaut3}
		\label{regaut3}
	}
	\subfigure[Bypass state 3 by adding concatenation transitions from states 1 and 2 to state 4. Remove state 3 and associated transitions.]
	{
		\includegraphics[scale=\myscale]{regaut4}
		\label{regaut4}
	}
%	
%	\subfigure[Finally remove state 3 and associated transitions.]
%	{
%		\includegraphics[scale=\myscale]{regaut5}
%		\label{regaut5}
%	}
	\caption{RegexpAutomaton and removing state 3 from it.} \label{regaut}
\end{figure}
